Semi-Inclusive Deep Inelastic Scattering in Wandzura-Wilczek-type approximation

### 2018-07-20 tex/test-WW-type-00z_old.tex
final

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[b!]
\centering
%\includegraphics[width=0.45\textwidth]{\FigPath/AUTPretzelosity_x.pdf}  
%\includegraphics[width=0.45\textwidth]{\FigPath/AUTPretzelosity_PT.pdf}
\includegraphics[width=0.3\textwidth]{\FigPath/Screenshot-Fig-COMPASS-A_UT_Pr10-left-panel-up.png} \ 
\includegraphics[width=0.3\textwidth]{\FigPath/Screenshot-Fig-COMPASS-A_UT_Pr10-left-panel-down.png}
\includegraphics[width=0.3\textwidth]{\FigPath/AUTPretzelosity_HERMES_x.pdf}

\caption{\label{aut_h1tp_jlab} $A_{UT}^{\sin(3 \phi_h - \phi_S)}$  
	as a function of $x$ from preliminary COMPASS \cite{Parsamyan:2010se} 
	and HERMES \cite{Schnell:2010zza} in comparison to the best fit 
	(whose 1-$\sigma$ uncertainty band is compatible with zero) 
	from \cite{Lefky:2014eia}. For comparison the COMPASS plots
	show the model results \cite{Kotzinian:2008fe,Boffi:2009sh}.
	\TD{\sf screenshot of {\tt Fig-COMPASS-A\_UT\_Pr10.pdf} 
	which was previously shown in Fig.~\ref{autsinphi_jlab}. 
	Bakur: please, can you produce such plot with Alexei's 
	``best fit'' from \cite{Lefky:2014eia}?}}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[b!]
\centering
\includegraphics[width=0.45\textwidth]{\FigPath/UT_Pr10_pretzelosity_pip.pdf}  
\includegraphics[width=0.45\textwidth]{\FigPath/UT_Pr10_pretzelosity_pim.pdf}
\includegraphics[width=0.45\textwidth]{\FigPath/AUTPretzelosity_HERMES_x.pdf}

\caption{\label{aut_h1tp_jlab} $A_{UT}^{\sin(3 \phi_h - \phi_S)}$  
	as a function of $x$ from preliminary COMPASS \cite{Parsamyan:2010se} 
	and $A_{UT, < y >}^{\sin(3 \phi_h - \phi_S)}$ HERMES \cite{Schnell:2010zza} in comparison to the best fit 
	(whose 1-$\sigma$ uncertainty band is compatible with zero) 
	from \cite{Lefky:2014eia}. For comparison the COMPASS plots
	show the model results \cite{Kotzinian:2008fe,Boffi:2009sh}.
	\TD{\sf screenshot of {\tt Fig-COMPASS-A\_UT\_Pr10.pdf} 
	which was previously shown in Fig.~\ref{autsinphi_jlab}. 
	Bakur: please, can you produce such plot with Alexei's 
	``best fit'' from \cite{Lefky:2014eia}?}}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
